Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-03-18 paper/manuscript.Rmd
delete header
Update manuscript.Rmd

Regardless, oceanic swimming is relatively common among a small minority of our
marked population. Of the three collared individuals, two were collared on
Western Indian Island and the third was collared on Fogo Island. Inter-island
distances between Western and Eastern Indian Islands, and the smaller islands
around them, are shorter than those between Fogo Island and others (Figure 2).
Individuals that were born on or spend more time on these smaller islands may
swim between them more frequently than animals that spend most of their time on
Fogo Island. The forage limitation hypothesis is generally thought to apply
uniformly across populations, but individual caribou could evaluate the costs
and benefits of swimming to another island differently. It is possible that some
individuals, in our case ~10%, considered swimming to be less costly or
perceived competition or predation more acutely than their conspecifics.

**Summary and conclusion**

@@

Our observations add to the evidence that caribou can, and occasionally do, swim
in the ocean [e.g. @Miller1995; @Miller2002; @Jeffery2007; @Ricca2012]. Taken
together, we suggest that swimming is likely more common than previously thought
for caribou living on oceanic islands, and that forage limitation and the
associated density-dependent habitat selection is an ultimate explanation for
this phenomenon. Although our inference is limited to observations, islands
appear to represent discrete foraging patches for terrestrial animals that can
influence fitness via increased foraging opportunities. We also posit that
individuals can vary in their evaluation of costs and benefits of movement
between these habitat patches.

>>>>

Regardless, oceanic swimming is relatively common among a minority of
marked caribou. Of the three collared individuals that swam the most, two were collared on
Western Indian Island and the third was collared on Fogo Island. Inter-island
distances between Western and Eastern Indian Islands, and the smaller islands
around them, are shorter than those between Fogo Island and others (Figure 2).
Individuals that were born on or spend more time on these smaller islands may
swim between them more frequently than animals that spend most of their time on
Fogo Island. The forage limitation hypothesis is generally thought to apply
uniformly across populations, but individual caribou could evaluate the costs
and benefits of swimming to another island differently. It is possible that some
individuals, in our case ~10%, considered swimming to be less costly or
perceived competition or predation more acutely than their conspecifics.

@@

Our observations add to the evidence that caribou can, and occasionally do, swim
in the ocean [e.g. @Miller1995; @Miller2002; @Jeffery2007; @Ricca2012]. 
We suggest that swimming is likely more common than previously thought
for caribou living on oceanic islands, and that forage limitation and the
associated density-dependent habitat selection is an ultimate explanation for
this phenomenon. Although our inference is limited to observations, islands
appear to represent discrete foraging patches for terrestrial animals that can
influence fitness via increased foraging opportunities. We also posit that
individuals can vary in their evaluation of costs and benefits of movement
between these habitat patches.
